Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-31 paper/src/paper.tex
add paper preview.

Providing the computing infrastuctures needed to solve actual complex problems
arising in the various fields of modern society (including climate change,
health, green energy or security) is a strategic challenge. The main pillar to
address this challenge is to build extreme-scale parallel and distributed
platforms. The race for always more computing power and storage capacity does
not only lead to sophisticated specific exascale platforms, but the objective
of the community is to design efficient sustained Petascale platforms. This
large-scale evolution and the increasing complexity in both architecture and
applications create many scientific and technical problems. Accordingly, system
management software still has a long way to go. The existing job and resource
management softwares allow to run tens thousands jobs on hundreds thousands
cores. They are based on robust policies, however, despite their positive
properties of relative simplicity and their guarantee of no job starvation,
there is still room for improvement. We propose here to study how to tune the
ordering of the submission queues in the frame of the classical
EASY-BackFilling family of heuristics using two new online learning approaches
(an approach based on a simulator and an approach using multi-armed bandit).

Most common work in the literature consider \textit{a posteriori} optimization
of a scheduling algorithm on a (actual) data set.  The increasing amount and
diversity of data generated by large scale platforms motivate the community to
study more sophisticated policies that could leverage these data.  During the
last few years, there was an explosion of the number of works at the interface
of HPC and BigData fileds, dealing with learning algorithms .  Recent
sophisticated approaches developed \textit{ad hoc} supervised machine learning
algorithms for reducing uncertainty in problem parameters (e.g. job execution
times, memory requirements, etc.) via prediction.  However, only few works
study the impact of such techniques on the performances of the resource
manager.

Contrarily to most existing studies, which consider the learning of specific
parameters of a trace, we provide a complete system that uses feedback from the
system for adapting the whole behavior online.  Our focus within this work is
to learn how the management system behaves within the usual framework of
EASY-BF.  More precisely, we provide strategies for choosing the most
appropriate queue reordering policy used for job selection.  This approach is
assessed by an extensive resampling-based experimental campaign that uses 7
actual traces.

@@

Both these methods are evaluated with a specially developped simulator that is
open-sourced and packaged for the community.

@@

Our main results are as follows: The approach based on the simulator provides
very good results, close to the best policy in the search set. In essence, this
means that we are able to recover in an online fashion existing results that
divide average waiting times by factor of \textcolor{orange}{X} to
\textcolor{orange}{X}. Indeed, we show that the required sample sizes for
policy selection in batch schedulers are small enough for workload resampling to
be avoided in practice. The variant based on noisy data, which is closer to
actual conditions of uncertainties on both jobs and platform, behaves also very
well. The alternate approach based on a multi-armed bandit does also provide
reasonable results at a much lower cost, dividing the average waiting times by
a factor of \textcolor{orange}{X} to \textcolor{orange}{X}.

>>>>

Providing the computing infrastuctures needed to solve actual complex problems
arising in the various fields of modern society (including climate change,
health, green energy or security) is a strategic challenge. The main pillar of
the answer to this challenge is to build extreme-scale parallel and distributed
platforms. The never-ending race for more computing power and storage capacity does
not only lead to sophisticated specific Exascale platforms, but the objective
of the community is to design efficient sustained Petascale platforms. This
large-scale evolution and the increasing complexity in both architecture and
applications create many scientific and technical problems. Accordingly, system
management software still has a long way to go. The existing job and resource
management softwares allow to run tens of thousands of jobs on hundreds of thousands
of cores. They are based on robust policies, however, despite their positive
properties such as relative simplicity and prevention of job starvation,
there is still room for improvement. We propose here to study how to tune the
ordering of the submission queues in the frame of the classical
EASY-BackFilling family of heuristics using two new online learning approaches
(an approach based on a simulator and an approach using multi-armed bandit).

Most common work in the literature consider \textit{a posteriori} optimization
of a scheduling algorithm on a (actual) data set.  The increasing amount and
diversity of data generated by large scale platforms motivate the community to
study more sophisticated policies that could leverage these data.  During the
last few years, there was an explosion of the number of works at the interface
of HPC and BigData fields, dealing with learning algorithms. Recent
sophisticated approaches developed \textit{ad hoc} supervised machine learning
algorithms for reducing uncertainty in problem parameters (e.g. job execution
times, memory requirements, etc.) via prediction. However, only few studies
evaluate the impact of such techniques on the performances of the resource
manager.

Contrarily to most existing studies, which consider the learning of specific
parameters of a trace, we provide a complete system that uses feedback from the
system for adapting the whole behavior online.  Our focus within this work is
to learn how the management system behaves within the usual framework of
EASY-BF. More precisely, we provide strategies for choosing the most
appropriate queue reordering policy to be used for job selection. This approach
is assessed by an extensive resampling-based experimental campaign that uses 7
actual traces.

@@

Both of these methods are evaluated with a specially developped simulator that is
open-sourced and packaged for the community.

@@

Our main results are as follows: The approach based on the simulator provides
very good results, close to the best policy in the search set. In essence, this
means that we are able to recover in an online fashion existing results that
divide average waiting times by factor of \textcolor{orange}{X} to
\textcolor{orange}{X}. Indeed, we show that the required sample sizes for
policy selection in batch schedulers are small enough for workload resampling to
be avoided in practice. The variant based on noisy data, which is closer to
actual conditions of uncertainties on both jobs and platform, also behaves very
well. The alternate approach based on a multi-armed bandit also provides
reasonable results at a much lower cost, dividing the average waiting times by
a factor of \textcolor{orange}{X} to \textcolor{orange}{X}.
